Response time of a plasmonic distributed feedback laser in large-signal modulation regime

### 2019-05-06 DFB_Pulse_LaTeX/DFB_pulse_inProcess.tex
Second response, revised

We use the fact of the constancy of the EM field distribution to construct a single-mode model. To do this, we assume that there is a single collective mode, the EM field distribution of which coincides with the EM field distribution found in the numerical simulations of the multimode problem. Furthermore, we assume that the pumped active medium interacts only with such a single collective mode. Within these approximations, the system dynamics can be described by the following system of equations \cite{SiegmanLasers}:
\begin{gather} 
\dot n =  - 2{\gamma _a}n + 2{N_{\text{at}}}{\Omega _R}\varphi \label{ZE1}
\\
\dot \varphi = - \left( {{\gamma _a} + {\gamma _\sigma }} \right)\varphi + {\Omega _R}\left( {2nD + D + 1} \right)/2 \label{ZE2}
\\
\dot D =  - {\gamma _D}\left( {D + 1} \right) - 4{\Omega _R}\varphi, \label{ZE3}
\end{gather}
where $n$ is the number of photons in the collective mode, $D$ is the mean population inversion of pumped atoms of the active medium, $\varphi$ describes the mean energy flow from the active medium to the collective mode, and $N_{\text{at}}$ is the number of atoms of the active medium lying in the collective mode.
We suppose that the relaxation rate of the EM field in the collective mode is equal to the characteristic relaxation rate of the modes of the plasmonic structure, i.e., $\gamma_a \simeq 10^{12} \text{s}^{-1}$.
Note that the finite size of the pump beam can lead to appearing of edge effects and influence on the mode quality factor, see \cite{hakala2017lasing}.
In the single-mode model, we do not take into account these effects.
The typical relaxation rate of the population inversion of the active medium is $\gamma_D \simeq 10^9 \text{s}^{-1}$ while the phase relaxation rate is $\gamma_{\sigma}\simeq 10^{13} \text{s}^{-1}$.
Thus, the phase relaxation rate is much larger than other relaxation rates, $\gamma_\sigma \gg \gamma_a, \gamma_D$.
For this reason, one can adiabatically eliminate $\varphi$ from Eqs.~(\ref{ZE1})--(\ref{ZE3}) and obtain the conventional rate equations
\begin{gather} 
\dot n =  - 2 {\gamma _a}n + {N_{\text{at}}}\Omega _R^2\left( {2nD + D + 1} \right)/{\gamma _\sigma } \label{RE1}
\\
\dot D =  - {\gamma _D}\left( {D + 1} \right) - 2\Omega _R^2\left( {2nD + D + 1} \right)/{\gamma _\sigma } \label{RE2}
\end{gather}
As initial condition we take $D(0) = 1$ and $n(0) = 0$, i.e., all atoms are inverted and there are no photons in the mode.
The temporal dynamics of such a system is well-known \cite{SiegmanLasers}; it is shown in Fig.~\ref{fig4}.

@@

To sum up, there is the diameter of the pump beam, $d_{\text{beam}}^*$, necessary to achieve the short response time. This diameter is about the decay length of the EM field in the plasmonic structure and for the considered plasmonic laser is $\sim 15 \mu$m. The existence of the critical pump beam size gives the opportunity to reduce the energy consumption because further increase of the pump beam size does not shorten the response time.
In turn, if the area of the pump beam is small, there is the opportunity to reduce the size of the device.
Thus, the obtained results pave the way to creating ultrafast optoelectronic devices based on plasmonic lasers with low power consumption which have the potential of on-chip integration.

>>>>

We use the fact of the constancy of the EM field distribution to construct a single-mode model. To do this, we assume that there is a single collective mode, the EM field distribution of which coincides with the EM field distribution found in the numerical simulations of the multimode problem. Furthermore, we assume that the pumped active medium interacts only with such a single collective mode. Within these approximations, the system dynamics can be described by the following system of equations \cite{SiegmanLasers}:
\begin{gather} 
\dot n =  - 2{\gamma _a}n + 2{N_{\text{at}}}{\Omega _R}\varphi \label{ZE1}
\\
\dot \varphi = - \left( {{\gamma _a} + {\gamma _\sigma }} \right)\varphi + {\Omega _R}\left( {2nD + D + 1} \right)/2 \label{ZE2}
\\
\dot D =  - {\gamma _D}\left( {D + 1} \right) - 4{\Omega _R}\varphi, \label{ZE3}
\end{gather}
where $n$ is the number of photons in the collective mode, $D$ is the mean population inversion of pumped atoms of the active medium, $\varphi$ describes the mean energy flow from the active medium to the collective mode, and $N_{\text{at}}$ is the number of atoms of the active medium lying in the collective mode.
We suppose that the relaxation rate of the EM field in the collective mode is equal to the characteristic relaxation rate of the modes of the plasmonic structure, i.e., $\gamma_a \simeq 10^{12} \text{s}^{-1}$.
Note that the finite size of the pump beam can lead to the appearance of edge effects and influence on the mode quality factor, see \cite{hakala2017lasing}.
In the single-mode model, we do not take into account these effects.
The typical relaxation rate of the population inversion of the active medium is $\gamma_D \simeq 10^9 \text{s}^{-1}$ while the phase relaxation rate is $\gamma_{\sigma}\simeq 10^{13} \text{s}^{-1}$.
Thus, the phase relaxation rate is much larger than other relaxation rates, $\gamma_\sigma \gg \gamma_a, \gamma_D$.
For this reason, one can adiabatically eliminate $\varphi$ from Eqs.~(\ref{ZE1})--(\ref{ZE3}) and obtain the conventional rate equations
\begin{gather} 
\dot n =  - 2 {\gamma _a}n + {N_{\text{at}}}\Omega _R^2\left( {2nD + D + 1} \right)/{\gamma _\sigma } \label{RE1}
\\
\dot D =  - {\gamma _D}\left( {D + 1} \right) - 2\Omega _R^2\left( {2nD + D + 1} \right)/{\gamma _\sigma } \label{RE2}
\end{gather}
As initial condition we take $D(0) = 1$ and $n(0) = 0$, i.e., all atoms are inverted and there are no photons in the mode.
The temporal dynamics of such a system is well-known \cite{SiegmanLasers}; it is shown in Fig.~\ref{fig4}.

@@

In consequense, there is the diameter of the pump beam, $d_{\text{beam}}^*$, necessary to achieve the short response time. This diameter is about the decay length of the EM field in the plasmonic structure and for the considered plasmonic laser is $\sim 15 \mu$m. The existence of the critical pump beam size gives the opportunity to reduce the energy consumption because further increase of the pump beam size does not shorten the response time.
In turn, if the area of the pump beam is small, there is the opportunity to reduce the size of the device.
Thus, the obtained results pave the way to creating ultrafast optoelectronic devices based on plasmonic lasers with low power consumption which have the potential of on-chip integration.
